A holographic approach to the six-dimensional superconformal index

### 2022-10-14 fivebranes/intro.tex
intro

A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories. The full factorization structure is extremely rich, and in this paper, we only discuss a small part of it: the costalk at a point as a vector space. However, this inforamtion is enough to extract familiar quantities like the superconformal index.

Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction. Accordingly, the desired factorization algebras should serve to organize many of the mathematical structures associated to lower dimensional superconformal field theories.

@@

Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper.
Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory.
Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{brane}(N)$.
In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebra $\Obs_{brane}(N)$.

Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{brane}(N)$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
We can, however, restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.\footnote{In general this is given by some limit construction like for sheaves, but we will use a particularly nice model in the context of holomorphic-topological factorization algebras in this paper.}

\begin{expect}[Twisted holographic principle following \cite{CLsugra}]
There is a map of factorization algebras
\[
  (\Obs_{grav}|_{Y})^{!}\to \Obs_{brane}(N)
\]
that becomes an equivalence in the large $N$ limit.
\end{expect}

@@

In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{1-brane}$. We emphasize that we only consider the classical limit of this factorization algebra in this paper. However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}

@@

The next simplest application of our holographic approach is to describe the observables of the six-dimensional theory of type~$A_1$. 
Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $Z$ and pushforward along the norm map to obtain an associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$. We re-emphasize that in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory. At the quantum level, we expect that the algebra gets deformed twisted by a cocycle.

\begin{conj}
Let $\operatorname{Higgs}_{SL(2)} (S,W)$ denote the moduli space of $SL(2)$ Higgs bundles on the complex surface~$S$ where the Higgs fields has coefficients in the rank two bundle~$W$.
The associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$ (after turning on the twisting cocycle) acts on
  \beqn
  \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right) .
  \eeqn
\end{conj}

As in the abelian case, we may hilight some compatibilities with the usual AGT correspondence. For a particular choice of the input geometric data, the same Maurer-Cartan element in $\lie{osp}(6|2)$ deforms the associative algebra $\pi_{*}\Obs_{A_{1}}|_{\R_{>0}}$ to the Virasoro algebra $U(\operatorname{Vir})$. We again expect that for a judicious choice of $X$, the Hilbert space deforms to the equivariant cohomology of the moduli of rank 2 instantons on $\C^{2}$, and the action compatibly deforms to the action in the rank 2 case of the AGT correspondence.

>>>>

A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories. The full factorization structure is extremely rich, and in this paper, we only discuss a small part of it: the costalk at a point as a vector space---otherwise known as the space of local operators at the point. 
However, this information is enough to extract familiar quantities like the superconformal index.

%Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction. Accordingly, the desired factorization algebras should serve to organize many of the mathematical structures associated to lower dimensional superconformal field theories.

@@

Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper.
Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory.
Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{N-branes}$.
In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebras $\Obs_{N-branes}$.

Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{N-branes}$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
We can, however, restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.\footnote{In general this is given by some limit construction like for sheaves, but we will use a particularly nice model in the context of holomorphic-topological factorization algebras in this paper.}

\begin{expect}[Twisted holographic principle following \cite{CLsugra}]
After taking into account the backreaction, there is a map of factorization algebras
\[
  (\Obs_{grav}|_{Y})^{!}\to \Obs_{N-branes}
\]
that becomes an equivalence in the large $N$ limit.
\end{expect}

@@

In the main body of the paper, we show that this agrees, in the classical limit, with the factorization algebra we denoted $\cF_{-1}$ above. 
We emphasize that we only consider the classical limit of this factorization algebra in this paper. 
However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.
From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction, which we plan to do in future work.

@@

The next simplest application of our holographic approach is to describe the observables of the six-dimensional theory of type~$A_1$.
Our expectation is that the factorization algebra $\Obs_{A_1}$ is related to the gravitational-side factorization algebra that we denoted by $\cF_0$ above.
Precisely, on each individual open set of the threefold $U \subset Z$, our conjecture in this paper is that the cohomology of $\cF_0(U)$ and of $\Obs_{A_1}(U)$ are the same.
To obtain the full factorization algebra structure from the gravitational side we should again include effects of the backreaction.

Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $Z$ and pushforward along the norm map to obtain an associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$.

\begin{conj}
Let $\operatorname{Higgs}_{SL(2)} (S,W)$ denote the moduli space of $SL(2)$ Higgs bundles on the complex surface~$S$ where the Higgs fields has coefficients in the rank two bundle~$W$.
The associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$ acts on
  \beqn
  \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right) .
  \eeqn
\end{conj}

As in the abelian case, we may highlight some compatibilities with the usual AGT correspondence. 
For a particular choice of the input geometric data, the same Maurer-Cartan element in $\lie{osp}(6|2)$ deforms the associative algebra $\pi_{*}\Obs_{A_{1}}|_{\R_{>0}}$ to the Virasoro algebra $U(\operatorname{Vir})$. We again expect that for a judicious choice of $X$, the Hilbert space deforms to the equivariant cohomology of the moduli of rank 2 instantons on $\C^{2}$, and the action compatibly deforms to the action in the rank 2 case of the AGT correspondence.
